---
title: "Predicting Social Determinants of Health in Kansas and Western Missouri"
output: 
  flexdashboard::flex_dashboard:
    theme: 
      version: 4
runtime: shiny
---

```{r global, include=FALSE}
#Load Necessary Libraries, zipcodeR package was used to generate zipcode dataset
library(dplyr)
library(ggplot2)
library(plotly)
library(caret)
library(flexdashboard)
library(shinyWidgets)
#library(zipcodeR)
library(DT)
script.dir <- dirname(sys.frame(1)$ofile)
#Load Data
load("./OnlyModels_7_26_22.RData")

#Data Table Function To facilitate rendering
DataTableRendererXTab <- function(tempDataTable){
  datatable(tempDataTable,editable=FALSE, rownames=F, style='bootstrap',fillContainer = TRUE,
  options = list(dom = 't', pageLength = -1,scrollY = T,columnDefs = list(list(className = 'dt-right', targets = 1:2)), initComplete = JS(
        "function(settings, json) {",
        "$(this.api().table().header()).css({'font-size': '85%'});",
        "}")))%>%
  DT::formatStyle(colnames(tempDataTable),fontSize = '85%')
}
```

```{r}
#Get User Input Data
  UserModelData <- eventReactive(input$execute, {
  ADIFromZip = as.numeric(ADI_DATA[ADI_DATA$ZIP == as.character(input$myZIP),]$ADI_STATERNK[1]) 
  #Temp_Zipcode_Data = reverse_zipcode(as.character(input$myZIP))
  Temp_Zipcode_Data = filter(ZipCodeRData, zipcode == as.character(input$myZIP))
  BucketFromZip = case_when(
   Temp_Zipcode_Data$county == 'Cass County' & Temp_Zipcode_Data$state == 'MO' ~ 'Cass,MO',
   Temp_Zipcode_Data$county == 'Clay County' & Temp_Zipcode_Data$state == 'MO'  ~ 'Clay,MO',
   Temp_Zipcode_Data$county == 'Jackson County' & Temp_Zipcode_Data$state == 'MO' ~ 'Jackson,MO',
   Temp_Zipcode_Data$county == 'Johnson County' & Temp_Zipcode_Data$state == 'KS' ~ 'Johnson,KS',
   Temp_Zipcode_Data$county == 'Leavenworth County' & Temp_Zipcode_Data$state == 'KS' ~ 'Leavenworth,KS',
   Temp_Zipcode_Data$county == 'Wyandotte County' & Temp_Zipcode_Data$state == 'KS' ~ 'Wyandotte,KS',
   Temp_Zipcode_Data$county == 'Platte County' & Temp_Zipcode_Data$state == 'MO' ~ 'Platte,MO',
   TRUE ~ "Other")
    #Format User Input Data to Model input
    paste(Temp_Zipcode_Data$county,Temp_Zipcode_Data$state,sep = ",")
    InputData = data.frame(Bucket = BucketFromZip,
                           GENDER = input$myGender,
                           RACE = input$myRace,
                           ETHNICITY = input$myEthnicity,
                           AGE = input$myAge,
                           ADI_STATERNK = ADIFromZip
                           )
  print(InputData)
  InputData$Bucket = as.factor(InputData$Bucket)
  InputData$GENDER = as.factor(InputData$GENDER)
  InputData$RACE = as.factor(InputData$RACE)
  InputData$ETHNICITY = as.factor(InputData$ETHNICITY)
  InputData$AGE = as.numeric(InputData$AGE)
  InputData$ADI_STATERNK = as.numeric(InputData$ADI_STATERNK)
#Get Model Predictions Based on user selection
    switch(input$myModel,
     "Logistic" = list(
       (predict(eval(as.symbol(paste0("Logistic",'_ModelQ001'))), InputData, type="response") > Model_ThresholdsQ001[[1]]$threshold),
       (predict(eval(as.symbol(paste0("Logistic",'_ModelQ002'))), InputData, type="response") > Model_ThresholdsQ002[[1]]$threshold),
       (predict(eval(as.symbol(paste0("Logistic",'_ModelQ003'))), InputData, type="response") > Model_ThresholdsQ003[[1]]$threshold),
       (predict(eval(as.symbol(paste0("Logistic",'_ModelQ004'))), InputData, type="response") > Model_ThresholdsQ004[[1]]$threshold),
       (predict(eval(as.symbol(paste0("Logistic",'_ModelQ005'))), InputData, type="response") > Model_ThresholdsQ005[[1]]$threshold),
       (predict(eval(as.symbol(paste0("Logistic",'_ModelQ006'))), InputData, type="response") > Model_ThresholdsQ006[[1]]$threshold),
       (predict(eval(as.symbol(paste0("Logistic",'_ModelQ007'))), InputData, type="response") > Model_ThresholdsQ007[[1]]$threshold),
       (predict(eval(as.symbol(paste0("Logistic",'_ModelQ008'))), InputData, type="response") > Model_ThresholdsQ008[[1]]$threshold),
       (predict(eval(as.symbol(paste0("Logistic",'_ModelQ009'))), InputData, type="response") > Model_ThresholdsQ009[[1]]$threshold),
       (predict(eval(as.symbol(paste0("Logistic",'_ModelQ010'))), InputData, type="response") > Model_ThresholdsQ010[[1]]$threshold),
       (predict(eval(as.symbol(paste0("Logistic",'_ModelQ011'))), InputData, type="response") > Model_ThresholdsQ011[[1]]$threshold),
       (predict(eval(as.symbol(paste0("Logistic",'_ModelQ012'))), InputData, type="response") > Model_ThresholdsQ012[[1]]$threshold)),
                    
     "Bayesian-GLM" = list(
       (predict(eval(as.symbol(paste0("BGLM",'_ModelQ001'))), InputData, type="response") > Model_ThresholdsQ001[[2]]$threshold),
       (predict(eval(as.symbol(paste0("BGLM",'_ModelQ002'))), InputData, type="response") > Model_ThresholdsQ002[[2]]$threshold),
       (predict(eval(as.symbol(paste0("BGLM",'_ModelQ003'))), InputData, type="response") > Model_ThresholdsQ003[[2]]$threshold),
       (predict(eval(as.symbol(paste0("BGLM",'_ModelQ004'))), InputData, type="response") > Model_ThresholdsQ004[[2]]$threshold),
       (predict(eval(as.symbol(paste0("BGLM",'_ModelQ005'))), InputData, type="response") > Model_ThresholdsQ005[[2]]$threshold),
       (predict(eval(as.symbol(paste0("BGLM",'_ModelQ006'))), InputData, type="response") > Model_ThresholdsQ006[[2]]$threshold),
       (predict(eval(as.symbol(paste0("BGLM",'_ModelQ007'))), InputData, type="response") > Model_ThresholdsQ007[[2]]$threshold),
       (predict(eval(as.symbol(paste0("BGLM",'_ModelQ008'))), InputData, type="response") > Model_ThresholdsQ008[[2]]$threshold),
       (predict(eval(as.symbol(paste0("BGLM",'_ModelQ009'))), InputData, type="response") > Model_ThresholdsQ009[[2]]$threshold),
       (predict(eval(as.symbol(paste0("BGLM",'_ModelQ010'))), InputData, type="response") > Model_ThresholdsQ010[[2]]$threshold),
       (predict(eval(as.symbol(paste0("BGLM",'_ModelQ011'))), InputData, type="response") > Model_ThresholdsQ011[[2]]$threshold),
       (predict(eval(as.symbol(paste0("BGLM",'_ModelQ012'))), InputData, type="response") > Model_ThresholdsQ012[[2]]$threshold)),
     
     
     "Extreme Gradiant Boost" = list(
       (predict(eval(as.symbol(paste0("XGB",'_ModelQ001'))), InputData, type="prob")$Yes > Model_ThresholdsQ001[[3]]$threshold),
       (predict(eval(as.symbol(paste0("XGB",'_ModelQ002'))), InputData, type="prob")$Yes > Model_ThresholdsQ002[[3]]$threshold),
       (predict(eval(as.symbol(paste0("XGB",'_ModelQ003'))), InputData, type="prob")$Yes > Model_ThresholdsQ003[[3]]$threshold),
       (predict(eval(as.symbol(paste0("XGB",'_ModelQ004'))), InputData, type="prob")$Yes > Model_ThresholdsQ004[[3]]$threshold),
       (predict(eval(as.symbol(paste0("XGB",'_ModelQ005'))), InputData, type="prob")$Yes > Model_ThresholdsQ005[[3]]$threshold),
       (predict(eval(as.symbol(paste0("XGB",'_ModelQ006'))), InputData, type="prob")$Yes > Model_ThresholdsQ006[[3]]$threshold),
       (predict(eval(as.symbol(paste0("XGB",'_ModelQ007'))), InputData, type="prob")$Yes > Model_ThresholdsQ007[[3]]$threshold),
       (predict(eval(as.symbol(paste0("XGB",'_ModelQ008'))), InputData, type="prob")$Yes > Model_ThresholdsQ008[[3]]$threshold),
       (predict(eval(as.symbol(paste0("XGB",'_ModelQ009'))), InputData, type="prob")$Yes > Model_ThresholdsQ009[[3]]$threshold),
       (predict(eval(as.symbol(paste0("XGB",'_ModelQ010'))), InputData, type="prob")$Yes > Model_ThresholdsQ010[[3]]$threshold),
       (predict(eval(as.symbol(paste0("XGB",'_ModelQ011'))), InputData, type="prob")$Yes > Model_ThresholdsQ011[[3]]$threshold),
       (predict(eval(as.symbol(paste0("XGB",'_ModelQ012'))), InputData, type="prob")$Yes > Model_ThresholdsQ012[[3]]$threshold)),
     
     "Gradiant Boost" = list(
       (predict(eval(as.symbol(paste0("GBM",'_ModelQ001'))), InputData, type="prob")$Yes > Model_ThresholdsQ001[[4]]$threshold),
       (predict(eval(as.symbol(paste0("GBM",'_ModelQ002'))), InputData, type="prob")$Yes > Model_ThresholdsQ002[[4]]$threshold),
       (predict(eval(as.symbol(paste0("GBM",'_ModelQ003'))), InputData, type="prob")$Yes > Model_ThresholdsQ003[[4]]$threshold),
       (predict(eval(as.symbol(paste0("GBM",'_ModelQ004'))), InputData, type="prob")$Yes > Model_ThresholdsQ004[[4]]$threshold),
       (predict(eval(as.symbol(paste0("GBM",'_ModelQ005'))), InputData, type="prob")$Yes > Model_ThresholdsQ005[[4]]$threshold),
       (predict(eval(as.symbol(paste0("GBM",'_ModelQ006'))), InputData, type="prob")$Yes > Model_ThresholdsQ006[[4]]$threshold),
       (predict(eval(as.symbol(paste0("GBM",'_ModelQ007'))), InputData, type="prob")$Yes > Model_ThresholdsQ007[[4]]$threshold),
       (predict(eval(as.symbol(paste0("GBM",'_ModelQ008'))), InputData, type="prob")$Yes > Model_ThresholdsQ008[[4]]$threshold),
       (predict(eval(as.symbol(paste0("GBM",'_ModelQ009'))), InputData, type="prob")$Yes > Model_ThresholdsQ009[[4]]$threshold),
       (predict(eval(as.symbol(paste0("GBM",'_ModelQ010'))), InputData, type="prob")$Yes > Model_ThresholdsQ010[[4]]$threshold),
       (predict(eval(as.symbol(paste0("GBM",'_ModelQ011'))), InputData, type="prob")$Yes > Model_ThresholdsQ011[[4]]$threshold),
       (predict(eval(as.symbol(paste0("GBM",'_ModelQ012'))), InputData, type="prob")$Yes > Model_ThresholdsQ012[[4]]$threshold)),
     
     "Neural Net" = list(
       (predict(eval(as.symbol(paste0("NeuralNet",'_ModelQ001'))), InputData, type="prob")$Yes > Model_ThresholdsQ001[[5]]$threshold),
       (predict(eval(as.symbol(paste0("NeuralNet",'_ModelQ002'))), InputData, type="prob")$Yes > Model_ThresholdsQ002[[5]]$threshold),
       (predict(eval(as.symbol(paste0("NeuralNet",'_ModelQ003'))), InputData, type="prob")$Yes > Model_ThresholdsQ003[[5]]$threshold),
       (predict(eval(as.symbol(paste0("NeuralNet",'_ModelQ004'))), InputData, type="prob")$Yes > Model_ThresholdsQ004[[5]]$threshold),
       (predict(eval(as.symbol(paste0("NeuralNet",'_ModelQ005'))), InputData, type="prob")$Yes > Model_ThresholdsQ005[[5]]$threshold),
       (predict(eval(as.symbol(paste0("NeuralNet",'_ModelQ006'))), InputData, type="prob")$Yes > Model_ThresholdsQ006[[5]]$threshold),
       (predict(eval(as.symbol(paste0("NeuralNet",'_ModelQ007'))), InputData, type="prob")$Yes > Model_ThresholdsQ007[[5]]$threshold),
       (predict(eval(as.symbol(paste0("NeuralNet",'_ModelQ008'))), InputData, type="prob")$Yes > Model_ThresholdsQ008[[5]]$threshold),
       (predict(eval(as.symbol(paste0("NeuralNet",'_ModelQ009'))), InputData, type="prob")$Yes > Model_ThresholdsQ009[[5]]$threshold),
       (predict(eval(as.symbol(paste0("NeuralNet",'_ModelQ010'))), InputData, type="prob")$Yes > Model_ThresholdsQ010[[5]]$threshold),
       (predict(eval(as.symbol(paste0("NeuralNet",'_ModelQ011'))), InputData, type="prob")$Yes > Model_ThresholdsQ011[[5]]$threshold),
       (predict(eval(as.symbol(paste0("NeuralNet",'_ModelQ012'))), InputData, type="prob")$Yes > Model_ThresholdsQ012[[5]]$threshold)),
     
     "Random Forest" = list(
       (predict(eval(as.symbol(paste0("RandomForest",'_ModelQ001'))), InputData, type="prob")$Yes > Model_ThresholdsQ001[[6]]$threshold),
       (predict(eval(as.symbol(paste0("RandomForest",'_ModelQ002'))), InputData, type="prob")$Yes > Model_ThresholdsQ002[[6]]$threshold),
       (predict(eval(as.symbol(paste0("RandomForest",'_ModelQ003'))), InputData, type="prob")$Yes > Model_ThresholdsQ003[[6]]$threshold),
       (predict(eval(as.symbol(paste0("RandomForest",'_ModelQ004'))), InputData, type="prob")$Yes > Model_ThresholdsQ004[[6]]$threshold),
       (predict(eval(as.symbol(paste0("RandomForest",'_ModelQ005'))), InputData, type="prob")$Yes > Model_ThresholdsQ005[[6]]$threshold),
       (predict(eval(as.symbol(paste0("RandomForest",'_ModelQ006'))), InputData, type="prob")$Yes > Model_ThresholdsQ006[[6]]$threshold),
       (predict(eval(as.symbol(paste0("RandomForest",'_ModelQ007'))), InputData, type="prob")$Yes > Model_ThresholdsQ007[[6]]$threshold),
       (predict(eval(as.symbol(paste0("RandomForest",'_ModelQ008'))), InputData, type="prob")$Yes > Model_ThresholdsQ008[[6]]$threshold),
       (predict(eval(as.symbol(paste0("RandomForest",'_ModelQ009'))), InputData, type="prob")$Yes > Model_ThresholdsQ009[[6]]$threshold),
       (predict(eval(as.symbol(paste0("RandomForest",'_ModelQ010'))), InputData, type="prob")$Yes > Model_ThresholdsQ010[[6]]$threshold),
       (predict(eval(as.symbol(paste0("RandomForest",'_ModelQ011'))), InputData, type="prob")$Yes > Model_ThresholdsQ011[[6]]$threshold),
       (predict(eval(as.symbol(paste0("RandomForest",'_ModelQ012'))), InputData, type="prob")$Yes > Model_ThresholdsQ012[[6]]$threshold)),
     
     print("Invalid Model Selected") # Default Statement
     )
}, ignoreInit = FALSE, ignoreNULL = FALSE)
```

Model Predictions 
===================================== 

Sidebar {.sidebar data-width=380}
-----------------------------------------------------------------------
```{r}
#Display Picker Elements
pickerInput(inputId = "myGender", 
  label="Gender",
  choices = GenderOptions, 
  multiple = FALSE)
pickerInput(inputId = "myRace", 
  label="Race",
  choices = RaceOptions, 
  multiple = FALSE)
pickerInput(inputId = "myEthnicity", 
  label="Ethnicity",
  choices = EthnicityOptions, 
  multiple = FALSE)
numericInput(inputId ="myAge", label = "Age",
            min = 0, value = 35, step = 1)
numericInput(inputId ="myZIP", label = "ZIPCode",
            value = 66062, step = 1)
actionButton("execute", "Apply")
pickerInput(inputId = "myModel", 
  label="Model",
  choices = ModelOptions, 
  multiple = FALSE)
```

<!-- Display User Results -->

Column {data-width=400}
-----------------------------------------------------------------------

### Question 1: In the last 12 months, did you ever eat less than you should because there wasn't enough?
  
```{r}
renderValueBox({
  req(UserModelData())
  valueBox(value = ifelse(UserModelData()[1], "Yes", "No"),
           color = ifelse(UserModelData()[1], "warning","primary"),
           icon = "fa-cutlery")
})
```

### Question 2: In the last 12 months, has your utility company shut  off your service for not paying your bill?
 
```{r}
renderValueBox({
  req(UserModelData())
  valueBox(value = ifelse(UserModelData()[2], "Yes", "No"),
           color = ifelse(UserModelData()[2], "warning","primary"),
           icon = "fa-plug")
})
```

### Question 3: Are you worried that in the next 2 months, you may not have stable housing?

```{r}
renderValueBox({
  req(UserModelData())
  valueBox(value = ifelse(UserModelData()[3], "Yes", "No"),
           color = ifelse(UserModelData()[3], "warning","primary"),
           icon = "fa-bed")
})
```

### Question 4: Are you afraid you might be hurt in your home by someone you know?

```{r}
renderValueBox({
  req(UserModelData())
  valueBox(value = ifelse(UserModelData()[4], "Yes", "No"),
           color = ifelse(UserModelData()[4], "warning","primary"),
           icon = "fa-home")
})
```

### Question 5: Are you afraid you might be hurt in your apartment building or neighborhood?

```{r}
renderValueBox({
  req(UserModelData())
  valueBox(value = ifelse(UserModelData()[5], "Yes", "No"),
           color = ifelse(UserModelData()[5], "warning","primary"),
           icon = "fa-building")
})
```

### Question 6: Do problems getting childcare make it difficult for you to work or study?

```{r}
renderValueBox({
  req(UserModelData())
  valueBox(value = ifelse(UserModelData()[6], "Yes", "No"),
           color = ifelse(UserModelData()[6], "warning","primary"),
           icon = "fa-child")
})
```

Column {data-width=400}
-----------------------------------------------------------------------

### Question 7: In the last 12 months, have you needed to see a doctor, but could not because of cost?

```{r}
renderValueBox({
  req(UserModelData())
  valueBox(value = ifelse(UserModelData()[7], "Yes", "No"),
           color = ifelse(UserModelData()[7], "warning","primary"),
           icon = "fa-user-md")
})
```

### Question 8: In the last 12 months, did you skip medications to save money?

```{r}
renderValueBox({
  req(UserModelData())
  valueBox(value = ifelse(UserModelData()[8], "Yes", "No"),
           color = ifelse(UserModelData()[8], "warning","primary"),
           icon = "fa-plus-square")
})
```

### Question 9: In the last 12 months, have you ever had to go without health care?

```{r}
renderValueBox({
  req(UserModelData())
  valueBox(value = ifelse(UserModelData()[9], "Yes", "No"),
           color = ifelse(UserModelData()[9], "warning","primary"),
           icon = "fa-stethoscope")
})
```

### Question 10: Do you have problems understanding what is told to you about your medical conditions?

```{r}
renderValueBox({
  req(UserModelData())
  valueBox(value = ifelse(UserModelData()[10], "Yes", "No"),
           color = ifelse(UserModelData()[10], "warning","primary"),
           icon = "fa-universal-access")
})
```

### Question 11: Do you often feel that you lack companionship?
```{r}
renderValueBox({
  req(UserModelData())
  valueBox(value = ifelse(UserModelData()[11], "Yes", "No"),
           color = ifelse(UserModelData()[11], "warning","primary"),
           icon = "fa-paw")
})
```

### Question 12: If you answered YES to any questions above, would you like to discuss help? 
```{r}
renderValueBox({
  req(UserModelData())
  valueBox(value = ifelse(UserModelData()[12], "Yes", "No"),
           color = ifelse(UserModelData()[12], "warning","primary"),
           icon = "fa-info-circle")
})
```

<!-- Display AUCs for models -->

AUC
===================================== 

Column {.tabset}
-------------------------------------

### Q1

```{r}
DT::renderDT({DataTableRendererXTab(ROC_TableQ001)})
```

### Q2

```{r}
DT::renderDT({DataTableRendererXTab(ROC_TableQ002)})
```

### Q3

```{r}
DT::renderDT({DataTableRendererXTab(ROC_TableQ003)})
```

### Q4

```{r}
DT::renderDT({DataTableRendererXTab(ROC_TableQ004)})
```

### Q5

```{r}
DT::renderDT({DataTableRendererXTab(ROC_TableQ005)})
```

### Q6

```{r}
DT::renderDT({DataTableRendererXTab(ROC_TableQ006)})
```

### Q7

```{r}
DT::renderDT({DataTableRendererXTab(ROC_TableQ007)})
```

### Q8

```{r}
DT::renderDT({DataTableRendererXTab(ROC_TableQ008)})
```

### Q9

```{r}
DT::renderDT({DataTableRendererXTab(ROC_TableQ009)})
```

### Q10

```{r}
DT::renderDT({DataTableRendererXTab(ROC_TableQ010)})
```

### Q11

```{r}
DT::renderDT({DataTableRendererXTab(ROC_TableQ011)})
```

### Q12

```{r}
DT::renderDT({DataTableRendererXTab(ROC_TableQ012)})
```

<!-- Display ROCs for Models -->

ROC Curves
===================================== 

Column {.tabset}
-------------------------------------

### Q1

```{r}
renderPlotly({
ggplotly(Graph_Q001)
})
```

### Q2

```{r}
renderPlotly({
ggplotly(Graph_Q002)
})
```

### Q3

```{r}
renderPlotly({
ggplotly(Graph_Q003)
})
```

### Q4

```{r}
renderPlotly({
ggplotly(Graph_Q004)
})
```

### Q5

```{r}
renderPlotly({
ggplotly(Graph_Q005)
})
```

### Q6

```{r}
renderPlotly({
ggplotly(Graph_Q006)
})
```

### Q7

```{r}
renderPlotly({
ggplotly(Graph_Q007)
})
```

### Q8

```{r}
renderPlotly({
ggplotly(Graph_Q008)
})
```

### Q9

```{r}
renderPlotly({
ggplotly(Graph_Q009)
})
```

### Q10

```{r}
renderPlotly({
ggplotly(Graph_Q010)
})
```

### Q11

```{r}
renderPlotly({
ggplotly(Graph_Q011)
})
```

### Q12

```{r}
renderPlotly({
ggplotly(Graph_Q012)
})
```